\documentclass[11pt]{article}
\usepackage{epsfig,epsf,rotating,graphics,colordvi,color,a4}
\textwidth=16cm
\textheight=22cm
\begin{document}
\newcommand{\refpoint}[1]{\ \vspace{0.3cm}\\ {\em #1}\  \vspace{0.3cm}\\ }
\newcommand{\refit}[1]{\em #1}
\newcommand{\refitem}[1]{\item {\em #1} }
\newcommand{\todo}[1]{\ \\ {\bf To do: #1}\\}
\section*{Reviewer \#1:} 
\refpoint{The paper has been appreciably improved upon revision. However some further amend-
ments are needed to achieve a contribution worthy of publication.}
We happily recognize that the changes and extensions which have followed from the referees suggestions 
in the first revision have improved the paper crucially. We are truly grateful for this. 
\refpoint{The main issues to be resolved are with presentation. In particular, dimensionless
variables are said to be given as starred variables (see the beginning of page 5). However,
in most of sections 3 and 4 this rule is forgotten (see also “Specific Issues”). This should
be fixed.}
Yes, indeed, we are struggling with dimensions. It is rather common to start with dimensional variables, keep
them for a while, and then introduce dimensionless variables from a given point. It is also common to 
introduce a star or a hat for the dimensionless variable, and then ``omit the star from this point on''. Retainment the star/hat in a large number of expressions and figures is very cumbersome and decrease
the overall legibility, in our view.
Our main problem in this respect is that the experiment in section 3.2 is given with dimensions in
the original, and we want to comply with this. On the other hand 3.3 and 4 are best represented
without dimensions. The ``solitary wave'' section 3.1 is also best presented without dimensions, 
but it needs to be placed before 3.2. Hence, we shift a little back and forth.
To mitigate the problem we specify what is used where more thoroughly.
\begin{itemize}
\item The dimension/dimensionless issue is addressed in the introduction.
\item We elaborate on scaling in the start of section 2
\item It is specified in the beginning of each subsection wether dimensions are used or not
\item Likewise, we specify in each figure.
\item Also the use of $A/h$ is a little untidy. We introduce a normalized mesure, $\alpha$, for
the amplitude of the incident wave.
\item we have gone through every expression and figures in order to clean up with respect to
dimensions.
\end{itemize}
    
\section*{Specific issues}
\begin{enumerate}
\refitem{ Abstract. Where appropriate, e.g. in the Abstract, reference to the model not being
fully nonlinear should be added;}\\
We agree. It now stated ``On the other hand, in the selected formulation only some non-linearity is retained in
the dispersion term. ......
Even though the equations of BoussClaw are not fully nonlinear they perform far better
than standard Boussinesq equations with only linear dispersion terms.''
 \refitem{ page 5, lines 2-3. Mention should be added that dimensionless (or normalized vari-
ables) are starred;}
Yes. This is done. In addition the whole issue is somewhat elaborated in the revision.
\refitem{ page 5, line 5. $u^* = \sqrt{gh_0}$ is a velocity scale, rather than a normalized velocity.
Please, amend;}
t's done.
\refitem{ page 6, lines 2-5. The definition of $w$ (vertical velocity, I guess) is missing. Please,
amend;}
No, $w$ is not the verical velocity, but a dummy variable employed to define the operator.
This is now explicitly stated in the text.
\refitem{ page 10, lines 1-13. I believe that the threshold depth is $d = 10^{−4}$m. If so, please,
amend;
Also be aware of theoretical and numerical issues related with the use of frictional-
type terms at the shoreline (e.g. Antuono et al., 2012);}
The $d$ was imprecise/wrong. The correct expression is slightly different from the one suggested by
the referee, namely $d=10^{−4}h_0$.\\
Concerning, Antuono et al: Both this reference and a very brief discussion of the effect of bottom friction on 
the withdrawal were omitted by mistake. It is now in place at the end of section 3.3.2.
\todo{New figure 11, discuss the looks}

\refitem{ page 12, last paragraph. Are energies here dimensional or dimensionless? In the
former case units should be given in plots, in the latter case variables should be
starred;}
Yes, the energies are dimensionless. For the relative errors in the right panel this does not matter, but
for the left panel it does. The caption and the text of section 3.1 is changed. 
\refitem{ figures 6, 7, 8, 9, 10, 11, 12, 13, 14, 15 and related text. Dimensionless variables
(elevation, space, time, etc.) should be starred;}
The stars may be cumbersome in the figures. We have tried to incoporate them when feasible in the figurs, but
do also discuss this in the captions. In the text wea have changed to starred quantities.
\todo{Change what figurs  are possible. Change all the text} 
\refitem{ page 23, lines 7-8. The meaning of this sentence is unclear to me. Please, clarify;}
Sorry. The text was not well formed. Hopefully, it is clearer now. 
\refitem{ page 25, lines 9-10. If I read well figure 15, $E_0$ of BoussClaw remains almost constant,
its increase being 3 − 4\% of the value attained using NLSW. Hence, I would not
speak of a “significant increase”;}
Agreed. We have changed to ``slightly, but noticeably,''
\refitem{ page 32, second half of the page. It is here said that the energy of a wave can be
approximated as $e = (e0+e1+O(\mu^4))$. However, inspection of definitions (B.2) and
(B.3) suggests that $e$ is reduced by the “equilibrium energy” $\rho gh^2/2$, which does
not appear in (B.2) and (B.3). Please, clarify;}
The text is amended. However, there was an error when we have runup or draw-down.
\todo{Discuss the the computation and the swash zone. Recompute the energies.}
\refitem{ page 33, last line of Appendix B.2. What does “$x_a$ and $x_b$ denote the limitations of
the wetted region” mean? Please, give clear definitions of $x_a$ and $x_b$.}
The objection is in fact deeper than it may appear. The integral for the total energy is modified and the 
limits more clearly explained.
\end{enumerate}
\bibliographystyle{plain}  % typesettingsformatet
\bibliography{mybibfile.bib}
\end{document}


